### 2018-02-01 includes/appendix.tex
Fixed logical issues.

We will make the folowing simplifications for our proofs:
\begin{itemize}
  \item
    Since many of the operators can be expressed in terms of other, our
    proofs will only consider a subset of the operators. In particular we will
    drop the following:
    \begin{itemize}
      \item \texttt{|} (boolean or)
      \item \texttt{=} for boolean expressions
      \item \texttt{<=}, \texttt{>}, \texttt{>=}
      \item \texttt{str.prefix}, \texttt{str.suffix}, \texttt{str.at}
      \item \texttt{str.contains}
      \item \texttt{re.range}
    \end{itemize}

@@

The proofs all follow a very similar structure. For each transformation
\texttt{Trans}, we show that a problem instance $P$ is satisfiable by a model $m$
if and only if $\texttt{Trans}(P)$ is satisfiable by $\texttt{Trans}(m)$, where
$\texttt{Trans}(M)$ is the transformation applied to all the constants in the
model $m$. In other words, we show that $\eval (P) = \eval (\texttt{Trans}(P))$.
This is proven using a straightforward induction on the structure of problem
instances.

\texttt{Multiply} has a weaker guarantee; it takes satisfiable problems to
satisfiable problems. For instance, $y<x<y+1$ is UNSAT, but multiplying by 2
transforms the problem into $y<x<y+2$ which is SAT. For \texttt{Multiply}, we
prove that if $\eval (P)$ is \texttt{true}, then, $\eval \texttt{Multiply}(P)$
is also \texttt{true}.

>>>>

We will make the folowing simplifications for our proofs:
\begin{itemize}
  \item
    Since many of the operators can be expressed in terms of other, our
    proofs will only consider a subset of the operators. In particular we will
    drop the following:
    \begin{itemize}
      \item \texttt{|} (boolean or)
      \item \texttt{=} for boolean expressions
      \item \texttt{<=}, \texttt{>}, \texttt{>=}
      \item \texttt{str.prefixof}, \texttt{str.suffixof}, \texttt{str.at}
      \item \texttt{str.contains}
      \item \texttt{re.range}
    \end{itemize}

@@

The proofs all follow a very similar structure. For each transformation
\textit{Trans}, we show that a problem instance $P$ is satisfiable by a model $m$
if and only if $\textit{Trans}(P)$ is satisfiable by $\textit{Trans}(m)$, where
$\textit{Trans}(M)$ is the transformation applied to all the constants in the
model $m$.

To show the above, we show that for all expressions $e$, $\textit{Trans}(\eval
(e)) = \eval (\textit{Trans}(e))$. This is proven using a straightforward
induction on the structure of expressions. Since the transformations fix
boolean constants, we have, $\textit{Trans}(\eval (P)) = \eval (P)$, and hence
if the original problem is satisfiable then the transformed problem is also
satisfiable.

For transformations that have an inverse, such as \textit{Translate}
and \textit{Reverse} this also shows that if the transformed problem is
satisfiable, then the original problem is satisfiable. This proves that these
transformations are equisat transformations. \textit{Multiply} does not have an
inverse and hence it only guarantees to take satisfiable problems to satisfiable
problems. This can be seen in the problem instance $y<x<y+1$ which is UNSAT, but
multiplying by 2 transforms the problem into $y<x<y+2$ which is SAT.
